Viscous Erosion in Porous Media

### 2018-01-14 docs/methods/erosion_methods.tex
NM
small changes to near singular section

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
viscous flow.  The boundary conditions are a constant pressure drop that
creates a flow from the left to right.  The rate of erosion is
proportional to the shear stress which is equivalent to the vorticity
evaluated on the bodies.  The colors represent the vorticity, so regions
with large vorticity (in magnitude) are regions where the flow will
erode the fastest.}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Near-singular integration}
\label{sec:NSI}
To accurately compute the velocity~\eqref{eqn:velocityDLP},
vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
at points $\xx \in \Omega$, we adopt a near-singular integration scheme
based entirely on upsampling.  We are only interested in computing the
velocity and vorticity for visualizing the flow, and it is not necessary
that we resolve the integrands for arbitrarily close target points

Computing the velocity, pressure, and vorticity at a point $\xx \in
\Omega$ requires evaluating the layer potential
\begin{align*}
  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy,
\end{align*}
where $\phi$ is either the velocity, pressure, or vorticity, and the
kernel $K$ are defined in
equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
or~\eqref{eqn:pressureDLP}.  This integral is approximated with a
trapezoid rule,
\begin{align}
  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
  \label{eqn:layerPotential}
\end{align}
where $q$ contains the quadrature weights, Jacobian, and density
function.  Note that this sum can only be computed once
equation~\eqref{eqn:completed_BIE} has been solved for the density
function $\eeta$.  Based on numerical experiments, the error of the
$N$-point trapezoid rule is acceptable for points $\xx$ that are more
than 5 arclength spacings from $\bd\Omega$.

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
viscous flow.  The boundary conditions are a constant pressure drop that
creates a flow from the left to right.  The rate of erosion is
proportional to the shear stress which is equivalent to the vorticity
evaluated on the bodies.  The colors represent the vorticity, so regions
with large vorticity (in magnitude) are regions where the flow will
erode the fastest.}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Near-singular integration}
\label{sec:NSI}
The layer potentials for the~\eqref{eqn:velocityDLP},
vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
need to be evaluated at points $\xx \in \Omega$. We write the general
layer potential as
\begin{align}
  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy.
  \label{eqn:genericLP}
\end{align}
Since the integrand is periodic and smooth, the trapezoid rule
guarantees spectral accuracy.  However, when the target point $\xx$ is
close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy
of the trapezoid rule deteriorates unless a large number of
discretization points are used.  We are only interested in computing the
velocity, vorticity, and pressure to visualize the flow, so it is not
necessary that we resolve the integrands for arbitrarily close target
points

The layer potential~\eqn{eqn:genericLP} is approximated with the
trapezoid rule 
\begin{align}
  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
  \label{eqn:layerPotential}
\end{align}
where $q$ contains the quadrature weights, Jacobian, and density
function.  Based on numerical experiments, the error of the $N$-point
trapezoid rule is acceptable for points $\xx$ that are more than 5
arclength spacings from $\bd\Omega$.
